# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
activity <- read.csv("activity.csv", header=TRUE)
```


## What are the mean and median total number of steps taken per day?
```{r}
daysum <- tapply(activity$steps, activity$date, sum, na.rm=TRUE)
daysum <- as.data.frame(daysum)
daymean <- mean(daysum$daysum)
daymedian <- median(daysum$daysum)
```

### Mean total number of steps taken per day: `r daymean`
### Median total number of steps taken per day: `r daymedian`


## What is the average daily activity pattern?
```{r}
intervalmean <- tapply(activity$steps, activity$interval, mean, na.rm=TRUE)
intervalmean <- as.data.frame(intervalmean, row.names=NULL)
intervalmean$interval <- rownames(intervalmean)
library(ggplot2)
qplot(interval, intervalmean, data=intervalmean, main="Average Steps Per Interval")
```

```{r}
sorted <- (intervalmean[order(intervalmean[,1], decreasing=TRUE),])
interval <- sorted[1,2]
stepavg <- sorted[1,1]
```

### The interval with the highest average number of steps is `r interval` with an average number of steps of `r stepavg`.


## Imputing missing values
```{r}

```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
```
